### 2014-10-09 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Update acknowlegment

The authors would like to thank XXXX. The authors would also like to thank John Culbertson of Central Valley Fire District, MT, for his assistance in compiling Table~\ref{tab:LODD}. Finally, the authors would like to thank Joseph Willi of the University of Illinois Urbana-Champaign for his assistance in creating dimensioned drawings of the structure.

>>>>

The authors would like to thank XXXX. The authors would also like to thank John Culbertson, Director of the Montana Fire Services Training School, for his assistance in compiling Table~\ref{tab:LODD}. Finally, the authors would like to thank Joseph Willi of the University of Illinois Urbana-Champaign for his assistance in creating dimensioned drawings of the structure.
